I/O simulation model with Linux page cache, integration and evaluation in SimGrid framework

### 2020-07-09 paper_io_sim.tex

			We model memory as a storage device, characterized with a capacity,
			a read bandwidth and a write bandwidth in most simulators
			\tristan{are the read and write bandwidths distinguished in simgrid?
			we should also talk about latency}. We refer to existing simulation
			models for storage devices, to simulate bandwidth sharing for
			parallel accesses \tristan{we should refer to related work, see
			comment there}.

			We introduce the concept of a data block as a unit to represent data
			cached in memory. A data block is a subset of file pages stored in
			page cache that were accessed in the same read or write
			operation. A data block
			has information about file name, block size, last access time, and a
			dirty flag that represents whether the data is clean (0) or dirty
			(1). A given file can have multiple data blocks in page cache. In
			addition, a data block can be split into an arbitrary number of
			smaller blocks, and data blocks can be merged together.
			\tristan{I reformulated this paragraph, please check}

@@

			\tristan{is this paragraph about read accesses or write accesses? I
			think you should make one for reads, and one for writes. The
			paragraph could start as follows: ``The simulated LRU lists are used
			as follows. When a file is accessed, \ldots ''} At the time when a
			file is accessed, some data of the file can be in cache or not. If
			accessed data is already cached, there are existing data blocks
			representing cached data in two page cache LRU lists. 
			As cached data is accessed again, these blocks are moved to 
			the active list, dirty blocks are merged into a bigger dirty block, 
			while clean data blocks are merged into another clean block. 
			If accessed data is not in cache, new blocks representing uncached data 
			are created and put into the top of the inactive list. 
			For more detail when uncached data is accessed, in the case of 
			reading file, as all uncached data is clean data, only one clean data 
			block is added to the inactive list.
			But in the case of writing uncached file data though cache, 
			this written data can be either dirty or clean. 
			Thus, at most two data blocks can be added to the inactive lists, 
			one is clean and one is dirty. 
			We also keep the size of the active list not larger than twice the size of 
			the inactive list as in the kernel. This is done by moving least recently 
			used blocks in the active list to the inactive list when the active list 
			grows. If only a part of a data block needs to be moved, 
			the block is split.

			Next, we simulate data flushing mechanism, which writes back 
			dirty data to disk. 
			The data flushing simulation function traverses the sorted inactive first, 
			and then the active list, looks for least recently used dirty blocks \tristan{, writes them to disk through the storage device model,} and 
			sets dirty flags of these blocks to 0 until the total flushed amount 
			reaches the amount to be flushed or there is no dirty data left in cache. 
			If the last flushed block is not entirely flushed, it is split into 
			two blocks, one that is flushed and one that remains dirty.
			The flushing time is simulated with storage model.

			For periodical flushing, our simulator searches in two page cache 
			LRU lists and flushes all the expired dirty data blocks. 
			A dirty data block is considered expired if the time from its last access 
			to current simulated time is longer than the predefined expire time. 
			Periodical flushing can be concurrent with cache read/write, 
			and sequential with disk read/write. When cache accesses and 
			periodical flushing are concurrent, flushing time is not added to simulated 
			time but the amount of flushed data is limited by flushing time. 
			When data is flushed in parallel with disk read/write, flushing time is 
			calculated by storage simulation model and total amount of data 
			to be flushed \tristan{This concurrency should be handled by the storage model, not the memory manager described here. 
			Rephrase the last sentences to explain this.}.

@@

            \tristan{very good writing Dzung, it reads very well now.}

@@

			\begin{algorithm}\caption{File read simulation}\label{alg:read}
				\small
				\begin{algorithmic}[1]
					\Input
        				\Desc{fn}{file name}
        				\Desc{fs}{file size (assumed to fit in memory)}
						\Desc{rt}{current simulated run time}
						\Desc{mm}{MemoryManager object}
						\Desc{rm}{memory read bandwidth}
						\Desc{sm}{storage simulation model}
   					\EndInput
   					\Output
						\Desc{rt}{simulated run time after the file is read}
   					\EndOutput
					\State rt = rt + mm.flush(2*fs - mm.cached(fn) - mm.evictable\_mem) 
					\State mm.evict(2*fs - mm.cached(fn) - mm.free\_mem) 
					\If {mm.cached(fn) $>$ 0}  \Comment{Read file cached data}
    					\State crt = mm.cache\_read(fn)  \Comment{Read data in cache}
    					\State mm.periodic\_flush(rt, crt) \Comment{Flush in duration = crt}
						\State rt = rt + crt
					\EndIf
					\If {mm.cached(fn) $<$ fs} \Comment{Read uncached data from disk}
						\State rt = rt + mm.periodic\_flush(rt) \Comment{Sequential flushing}
						\State mm.disk\_read(fs - mm.cached(fn), fn)
    					\State rt = rt + sm.read(fs - mm.cached(fn))
					\EndIf

					\State \Return rt

@@

			The algorithm to simulate file reads is described in 
			Algorithm~\ref{alg:read} \tristan{you should now remove the incrementation of simulation time, as the storage models will do that.
			Essentially, we neglect kernel time and assume that time is entirely spent in IO. It will simplify the algorithms further, which is also elegant. If you 
			agree, please revise the algorithm and its description accordingly, and do the same for algorithm 2.
			}.  
			In Linux systems with write-back storage devices, data can be either read 
			from cache with memory bandwidth or read from disk with disk bandwidth. 
			Therefore, total read time can be considered as a linear function 
			of the read time with each of these bandwidths, 
			enabling us to generalize reading process as two separate phases, 
			cache read and disk read. 
			When a simulated application reads a file, 
			it sends a file read request to IO Controller. 
			First, if there  is not enough memory available to store two
			copies of the file (one in cache, one in anonymous memory), the
			Memory Manager is called to flush dirty data to disk (line 10).
			This flushing is complemented by eviction by the Memory Manager (line 11). 
			Next, if the file is cached, either partially or entirely, the Memory Manager is 
			called to read and update the corresponding data blocks in cache (line 13). 
			During cache read, periodical flushing is called to flush dirty data if needed 
			and limited to cache read time \tristan{unclear, reword} (line 14).
			Cache read time is then added to total simulated time (line 15) \tristan{this should be part of the storage model}. 
			If file is not cached or partially cached, a disk read is required (line 17). 
			Periodical flushing is called once again, but not time-limited since 
			data flushing and disk read are sequential, and the flushing time is 
			added to simulated time (line 18).
			Finally, data is read from disk to cache and managed by MemoryManager, 
			disk read time estimated by the storage model is added to 
			total simulated run time (line 19-20).

			\begin{algorithm}\caption{File write simulation}\label{alg:write}
				\small
				\begin{algorithmic}[1]
					\Input
        				\Desc{fn}{file name}
        				\Desc{fs}{file size}
						\Desc{rt}{current simulated run time}
						\Desc{mm}{MemoryManager object}
						\Desc{wm}{memory write bandwidth}
						\Desc{sm}{storage simulation model}
   					\EndInput
   					\Output
						\Desc{rt}{simulated run time after the file is read}
   					\EndOutput
   					\State pft = mm.periodic\_flush(rt)
					\State remain\_dirty = dirty\_ratio * mm.avail\_mem - mm.dirty
					\State mem\_amt = min(fs, remain\_dirty)
					\If {remain\_dirty $>$ 0} \Comment{Write with memory bandwidth}
    					\State mm.evict(mem\_amt - mm.free\_mem)
    					\State mm.periodic\_flush(rt, mm.write\_time(mem\_amt)) 
    					\State rt = rt + mm.write(fn, mem\_amt)
    				\EndIf
    				\State rt = rt + max(mem\_amt / wm, pft) \Comment{Concurrent processes}
					\If {mem\_amt $<$ fs}  \Comment{Write with disk bandwidth}
						\State mm.flushed(fs - mem\_amt)  \Comment{Concurrent flushing}
						\State mm.evict(fs - mem\_amt  - mm.free\_mem) 
						\State mm.write(fn, min(fs - mem\_amt, mm.free\_mem))
						\State rt = rt + sm.write(fs - mem\_amt)
					\EndIf

					\Return rt

@@

			Algorithm~\ref{alg:write} describes our simulation of file write. 
			Initially, periodical flushing is called to flush expired dirty data 
			at the beginning of the write (line 10).
			Similar to the file read simulation, a file can also be written with 
			two different bandwidths, memory bandwidth and disk bandwidth. 
			Files can be written with memory bandwidth before the amount 
			of dirty data reaches dirty\_ratio. Thus, our algorithm initially checks 
			the amount of file data that can be written with memory write 
			bandwidth (line 11-12).
			If this amount is greater than 0, MemoryManager is asked to evict 
			data from cache if needed (line 14).
			Next, periodical flushing flushes data during cache write because they 
			can be concurrent (line 15). Then, data is written to cache with memory 
			bandwidth, write time is simulated and added to total simulated 
			time (line 16).
			The amount of data that is not written with memory bandwidth is written 
			with disk bandwidth (line 18). 
			Now, the dirty ratio threshold is reached, we have to flush and evict 
			data from cache as much as possible so that 
			the remaining data can be written to cache (line 20-21). 
			Here, MemoryManager does not guarantee that the amount of flushed 
			and evicted data is enough for the remaining data. In the case it is 
			less than the required amount, the remaining data is written to cache 
			but then can be flushed and evicted right away. Thus, the amount 
			of remaining data that is written and kept in cache after the write 
			is limited by the amount free memory (line 22). 
			Finally, the write time is simulated, added to the total time and 
			returned to simulated applications (line 23).

@@

			To validate our simulation model, we create a simple prototype
			simulator independently of existing simulation frameworks and libraries. 
			This enables us to evaluate the accuracy and correctness of our 
			model in a simple scenario before integrating it in the more complex SimGrid environment. 
			In this prototype we use the following basic storage model, used for both memory and disk: 
			\begin{align*}
				& t_{mr} = D / r_m \\ 
				& t_{mw} = D / w_m\
			\end{align*}

			where:
			\begin{itemize}
				\item $t_{mr}$ is the time to read data from memory
				\item $t_{mw}$ is the time to write data to memory
				\item $D$ is the amount of data to read/write
				\item $r_m$ is the memory read bandwidth
				\item $w_m$ is the  memory write bandwidth
			\end{itemize}			
			\tristan{if this applies equally to memory and disk, use ``device'' instead of ``memory''}

			Since bandwidth sharing is not simulated, this prototype doesn't support concurrency: it is limited 
			to single-threaded pipelines running on systems 
			with a single-core CPU. \tristan{the following aren't resulting from the lack of bandwidth sharing simulation, these are more general limitations, I think we 
			should remove them: , a single local storage device, and all input and 
			output files are stored locally.} We use it in a first validation of our simulation model,
			against a real sequential pipeline running on
			a real system.

			Having our model validated, we create simulators for different use cases 
			using the current version of SimGrid and the SimGrid version that is 
			extended with our model. To simulate our pipelines and system, we leverage the Workflow Management System Simulation Workbench (WRENCH~\cite{wrench}), a framework  
			built over SimGrid.
		    We compare the results of the simulators with
			original SimGrid and extended SimGrid with the results of real
			pipelines on a real system \tristan{this will have to be updated with a description of extended SimGrid, 
			you should add a placeholder for this description.}.

			We use Python 3.7 to implement the simple simulator, SimGrid 3.25
			and Wrench 1.6 for SimGrid simulators. SimGrid source code is
			available at \url{https://framagit.org/simgrid/simgrid}, and WRENCH
			is at \url{https://github.com/wrench-project/wrench}.
			\tristan{You should also add the URL of your Python prototype}

@@

			The goal of our experiments is to evaluate our write-back cache
			simulation in single-threaded and multi-threaded applications
			accessing data on different types of file system. We use a pipeline
			of sequential tasks where each task reads an input file, increments
			every byte of the input to emulate real processing and avoid caching
			effects, and writes the result to disk. The output of the previous
			task is the input of the next task. We also use a real application pipeline, to evaluate the applicability of our
			simulation model \tristan{add a placeholder to describe the real pipeline here}.

			The simplest execution scenario is single-threaded, where memory 
			bandwidth and disk bandwidth are dedicated. 
			This allows us to compare the detailed results in terms of read/write time, 
			memory states after every single task and, more importantly, validate our 
			simulation model \tristan{last sentence is convoluted, reword}.

			For multi-threaded applications, we vary the number of concurrent
			pipelines running on a multi-core host and writing to the same local
			disk. In this way, we evaluate our model with concurrent I/Os, when
			the device bandwidth is shared.

		    Since different storage types should also be taken into account, 
		    we conduct the next experiment with the same scenario as 
		    in the multi-threaded experiment, except that files are stored on a 
		    shared file system instead of local disk.

		    Finally, we consider a real pipeline from the neuroimaging domain. 
		    We simulate the pipeline with a simulated workflow in SimGrid 
			and compare the simulation results with the real results. 
			Because our work focuses on I/O time, we assume that CPU time is 
			correctly modeled and use the CPU time measured in the real pipelines 
			to setup our simulated workflow \tristan{the pipeline should be described, including the workflow engine if it's Dask.}.

			We use our dedicated cluster hosted at Concordia University to conduct the experiments. The cluster 
			consists of one login node, 8 compute nodes 
			and 4 storage nodes connected with two network switches. The login node 
			has one Intel(R) Xeon(R) Gold 6130 CPU @ 2.10GHz, 128GiB of RAM, 1.8TB 
			of storage of XFS file system, 13GB of tmpfs file system and 385 TB of 
			Lustre shared file system. Each compute node has two 16 cores Intel(R) 
			Xeon(R) Gold 6130 CPU @ 2.10GHz, 256 GB of RAM and 6 SSDs, 450GB each 
			with XFS file system, 378GB of tmpfs and 126GB of devtmpfs file system.
			Lustre file system is configured with one metadata target with 854GB 
			of storage, 44 object storage targets with 8.7TB of storage each. 
			The cluster is run on CentOS 8.1 with the Slurm Workload Manager installed. We use 
			\textbf{\textit{atop}} and \textbf{\textit{collectl}} as tools to monitor 
			and collect data of memory, page cache status and disk throughput on 
			the cluster. The cluster nodes are connected with ... 
			\textcolor{red}{[network description here]}
			\tristan{mention the number of disks on all nodes. Maybe add a diagram.}

			\tristan{I don't think you need an intro paragraph for each experiment, as you did above, AND then subsections. I'd just make a single paragraph or sub-section.}
			\subsubsection{Single-threaded evaluation}

				In this experiment, our goal is to validate our model by comparing 
				the simulation results of the simple Python simulator with results of 
				a simulator implemented with original SimGrid, a simulator 
				implemented with SimGrid integrated with our model, and a real pipeline 
				running of the cluster. 
				The pipeline consists of three tasks, each task reads a file, 
				increases every byte and writes output file to local disk. 
				We use the input sizes of 20 GB, 50 GB, 75 GB and 100 GB, run 
				the pipeline on the cluster, measure the CPU time of the pipeline 
				with each input to simulate the pipeline with the simulators.

@@

				In the second experiment, we evaluate the simulator in concurrent I/O 
				with a multi-threaded application. As we run the pipelines on 
				only one compute node of the cluster, which has upto 32 cores per node,  
				we create 32 input files with the size of 3GB each and vary the number of 
				concurrent pipelines from 1 to 32. 
				Because multi-threaded simulator implementation in Python is 
				expensive, and we have our model integrated in SimGrid, 
				we only compare the results of simulators with original SimGrid, 
				SimGrid integrated with our model and and real pipelines. 
				The results are compared in total makespan of the pipelines, 
				cumulative read time and cumulative write time.

@@

			\subsubsection{Simulation of a real application}
				A real pipeline (for example a pipeline with nighres)

>>>>

			We leverage existing storage simulation models to simulate the memory,
			which is characterized with capacity, read and write bandwidths. 
			This can be done when disks are modeled with distinguished read/write 
			bandwidths and negligible disk latency, which is applicable to memory 
			\cite{lebre2015}. In addition, leveraging existing disk models allows us 
			to take advantage of bandwidth sharing between concurrent disk I/O to 
			simulate parallel memory accesses.\tristan{we should refer to related work, 
			see comment there}.

			We introduce the concept of a data block as a unit to represent data
			cached in memory. A data block is a subset of file pages stored in
			page cache that were accessed in the same read or write operation. 
			A data block has information about file name, block size, last access 
			time, and a dirty flag that represents whether the data is clean (0) 
			or dirty (1). 
			A given file can have multiple data blocks in page cache. In
			addition, a data block can be split into an arbitrary number of
			smaller blocks, and data blocks can be merged together.

@@

			The simulated LRU lists are used as follows. When a file is read, 
			file data can be partially cached, completely cached, or uncached. 
			For cached data, there are existing data blocks representing 
			this data in two page cache LRU lists. 
			As this cached data is accessed again, these blocks are moved to 
			the active list, dirty blocks are merged into a bigger dirty block, 
			while clean data blocks are merged into another clean block. 
			If data read is not in cache, a clean block representing uncached data 
			is created and put into the top of the inactive list.

			In the case of writing data, we can assume that all written data 
			is uncached. After data is written, some can remain dirty, some is 
			clean after being flushed. 
			Thus, at most two data blocks can be added, one is clean and one 
			is dirty, to the inactive list.

			We also keep the size of the active list not larger than twice the size of 
			the inactive list as in the kernel 
			\cite{gorman2004understanding, linuxdev3rd2010}. 
			This is done by moving least recently used blocks in the active list 
			to the inactive list when the active list grows. If only a part of a data 
			block needs to be moved, the block is split.

			Next, we simulate data flushing mechanism, which writes back 
			dirty data to disk. 
			The data flushing simulation function traverses the sorted inactive first, 
			and then the active list, looks for least recently used dirty blocks, 
			writes them to disk through the storage device model, and 
			sets dirty flags of these blocks to 0 until the total flushed amount 
			reaches the amount to be flushed or there is no dirty data left in cache. 
			If the last flushed block is not entirely flushed, it is split into 
			two blocks, one that is flushed and one that remains dirty.
			The flushing time is simulated with storage model.

			For periodical flushing, our simulator searches in two page cache 
			LRU lists and flushes all the expired dirty data blocks. 
			A dirty data block is considered expired if the time from its last access 
			to current simulated time is longer than the predefined expire time. 
			Periodical flushing can be concurrent with cache read/write, 
			and sequential with disk read/write. When cache accesses and 
			periodical flushing are concurrent, flushing time is not added to simulated 
			time but the amount of flushed data is limited by flushing time. 
			When data is flushed in parallel with disk accesses, the concurrency 
			is handled by the storage model used as memory, and flushing time 
			is simulated with the amount of flushed data by this model.

@@

@@

			\begin{algorithm}\caption{File read simulation}\label{alg:read}
				\small
				\begin{algorithmic}[1]
					\Input
        				\Desc{fn}{file name}
        				\Desc{fs}{file size (assumed to fit in memory)}
						\Desc{mm}{MemoryManager object}
						\Desc{sm}{storage simulation model}
   					\EndInput
					\State mm.flush(2*fs - mm.cached(fn) - mm.evictable\_mem) 
					\State mm.evict(2*fs - mm.cached(fn) - mm.free\_mem) 
					\If {mm.cached(fn) $>$ 0}  \Comment{Read file cached data}
					    \State mm.periodic\_flush() \Comment{Flush during cache read}
    					\State mm.cache\_read(fn) 
					\EndIf
					\If {mm.cached(fn) $<$ fs} \Comment{Read uncached data from disk}
						\State mm.periodic\_flush() \Comment{Sequential with disk read}
						\State mm.add\_to\_cache(fs - mm.cached(fn), fn)
    					\State sm.read(fs - mm.cached(fn))
					\EndIf

@@

			The algorithm to simulate file reads is described in 
			Algorithm~\ref{alg:read}.   
			In Linux systems, data can be either read from cache with memory bandwidth 
			or read from disk with disk bandwidth. 
			Therefore, total read time can be considered as sequential reads with 
			these different bandwidths, enabling us to generalize reading process as 
			two separate phases, cache read and disk read. 
			When a simulated application reads a file, it sends a file read request 
			to IO Controller. 
			First, if there is not enough memory available to store two
			copies of the file (one in cache, one in anonymous memory), the
			Memory Manager is called to flush dirty data to disk and simulate 
			flushing time with memory model (line 6).
			This flushing is complemented by eviction by the Memory Manager (line 7). 
			Next, if the file is cached, either partially or entirely, data is read from 
			cache first. Periodical flushing is triggered at the beginning of the 
			cache read to flush dirty data if some dirty data is expired (line 9).
			At the same time, Memory Manager is called to read data from cache, 
			and update the corresponding data blocks in cache (line 10). 
			The concurrency of periodical flushing and cache read is handled and 
			time is simulated by the memory and disk models.

			If file is not cached or partially cached, a disk read is required (line 12). 
			Periodical flushing is called again at the beginning of the disk read 
			(line 13), the storage model simulates the disk write with the remaining 
			amount of data (line 14), and data read from disk is added to cache 
			(line 15). Similar to cache read period, disk bandwidth sharing is handled 
			and time is simulated by storage models.

			\begin{algorithm}\caption{File write simulation}\label{alg:write}
				\small
				\begin{algorithmic}[1]
					\Input
        				\Desc{fn}{file name}
        				\Desc{fs}{file size}
						\Desc{mm}{MemoryManager object}
						\Desc{sm}{storage simulation model}
   					\EndInput
   					\State mm.periodic\_flush()
					\State remain\_dirty = dirty\_ratio * mm.avail\_mem - mm.dirty
					\State mem\_amt = min(fs, remain\_dirty)
					\If {remain\_dirty $>$ 0} \Comment{Write with memory bandwidth}
    					\State mm.evict(mem\_amt - mm.free\_mem)
    					\State mm.write(fn, mem\_amt) 
    				\EndIf
					\If {mem\_amt $<$ fs}  \Comment{Write with disk bandwidth}
						\State mm.flush(fs - mem\_amt)  \Comment{Concurrent with disk write}
						\State mm.evict(fs - mem\_amt  - mm.free\_mem) 
						\State mm.add\_to\_cache(fn, min(fs - mem\_amt, mm.free\_mem))
						\State sm.write(fs - mem\_amt)
					\EndIf

@@

			Algorithm~\ref{alg:write} describes our simulation of file write. 
			Initially, periodical flushing is called to asynchronously flush expired 
			dirty data at the beginning of the write (line 6).
			Similar to the file read simulation, a file can also be written with 
			two different bandwidths, memory bandwidth and disk bandwidth. 
			Data can be written with memory bandwidth before the amount 
			of dirty data reaches dirty\_ratio. Thus, our algorithm initially checks 
			the amount of data that can be written with memory write 
			bandwidth (line 7-8).
			If this amount is greater than 0, MemoryManager is asked to evict 
			data from cache to accommodate the written data if needed (line 10). 
			Then, cache write is simulated with memory model and data written is 
			added to page cache LRU lists (11).
			The amount of data that is not written with memory bandwidth is written 
			with disk bandwidth (line 13). 
			Now, the dirty ratio threshold is reached, we have to flush and evict 
			data from cache as much as possible so that 
			the remaining data can be written to cache (line 14-15). 
			Here, MemoryManager does not guarantee that the amount of flushed 
			and evicted data is enough for the remaining data. In the case it is 
			less than the required amount, the remaining data is written to cache 
			but then can be flushed and evicted right away. Thus, the amount 
			of remaining data that is written and kept in cache after the write 
			is limited by the amount free memory (line 16). 
			Finally, the disk write is simulated with the remaining amount of 
			data (line 17). As in the simulation of file read, all the concurrent 
			cache write and disk write are simulated by memory and disk models.

@@

			To validate our simulation model, we create a simple prototype
			simulator independently of existing simulation frameworks and libraries. 
			This enables us to evaluate the accuracy and correctness of our 
			model in a simple scenario before integrating it in the more complex SimGrid environment. 
			In this prototype we use the following basic storage model, used for both memory and disk: 
			\begin{align*}
				& t_{r} = D / b_r \\ 
				& t_{w} = D / b_w\
			\end{align*}

			where:
			\begin{itemize}
				\item $t_{r}$ is the data read time
				\item $t_{w}$ is the data write time
				\item $D$ is the amount of data to read/write
				\item $b_r$ is the read bandwidth of the device
				\item $b_w$ is the write bandwidth of the device
			\end{itemize}

			Since bandwidth sharing is not simulated, this prototype doesn't support 
			concurrency: it is limited to single-threaded pipelines running on systems 
			with a single-core CPU. We use it in a first validation of our simulation 
			model, against a real sequential pipeline running on a real system.
			Source code of our Python prototype is available at 
			https://github.com/big-data-lab-team/paper-io-simulation/tree/master/exp/pysim

			Having our model validated, we create simulators for different use cases 
			using the current version of SimGrid and the SimGrid version that is 
			extended with our model. To simulate our pipelines and system, we leverage 
			the Workflow Management System Simulation Workbench 
			(WRENCH~\cite{wrench}), a framework  built over SimGrid.
		    We compare the results of the simulators with
			original SimGrid and extended SimGrid with the results of real
			pipelines on a real system.

			\textcolor{red}{[Description, implementation of our SimGrid extension]}.

			We use Python 3.7 to implement the simple simulator, SimGrid 3.25
			and Wrench 1.6 for SimGrid simulators. SimGrid source code is
			available at \url{https://framagit.org/simgrid/simgrid}, and WRENCH
			is at \url{https://github.com/wrench-project/wrench}.

@@

			The goal of our experiments is to evaluate our write-back cache
			simulation in single-threaded and multi-threaded applications
			accessing data on different types of file system. We use a pipeline
			of sequential tasks where each task reads an input file, increments
			every byte of the input to emulate real processing and avoid caching
			effects, and writes the result to disk. The output of the previous
			task is the input of the next task. We also use a real application 
			pipeline, to evaluate the applicability of oursimulation model.

			We use our dedicated cluster hosted at Concordia University to conduct 
			the experiments. The cluster consists of one login node, 8 compute nodes 
			and 4 storage nodes connected with two network switches. The login node 
			has one Intel(R) Xeon(R) Gold 6130 CPU @ 2.10GHz, 128GiB of RAM, 1.8TB 
			of storage of XFS file system, 13GB of tmpfs file system and 385 TB of 
			Lustre shared file system. Each compute node has two 16 cores Intel(R) 
			Xeon(R) Gold 6130 CPU @ 2.10GHz, 256 GB of RAM and 6 SSDs, 450GB each 
			with XFS file system, 378GB of tmpfs and 126GB of devtmpfs file system.
			Lustre file system is configured with one metadata target with 854GB 
			of storage, 44 object storage targets with 8.7TB of storage each. 
			The cluster is run on CentOS 8.1 with the Slurm Workload Manager installed. 
			We use \textbf{\textit{atop}} and \textbf{\textit{collectl}} as tools to 
			monitor and collect data of memory, page cache status and disk throughput 
			on the cluster. 
			\textcolor{red}{[Add network description here, include number of disks 
			on all nodes ,maybe add a diagram]}

			\subsubsection{Single-threaded evaluation}

			The simplest execution scenario is single-threaded, where memory 
			bandwidth and disk bandwidth are dedicated. Our goal is to 
			compare the detailed simulation results of each task in the pipeline 
			including read/write time, memory status and then validate the correctness 
			of the simulation model.

			The pipeline used in this experiment consists of three tasks, 
			each task reads a file, increases every byte and writes output file 
			to local disk. 
			We use the input sizes of 20 GB, 50 GB, 75 GB and 100 GB, run 
			the pipeline on the cluster, measure the CPU time of the tasks  
			with each input and use it to simulate CPU time in the simulators .

			We simulate the pipeline with the Python prototype simulator, 
			a simulator implemented with original SimGrid and a simulator implemented 
			with SimGrid extended with our model.

@@

			In the second experiment, we evaluate the simulator in a concurrent I/O, 
			bandwidth-sharing scenario with a multi-threaded application. 			
			We vary the number of concurrent pipelines running on a multi-core host.

			All the task in the pipelines read input files from and write output files 
			to a local disk. 
			As a compute node of the cluster has 32 cores CPU and 256 GB of RAM,  
			we create 32 input files with the size of 3GB each and vary the number of 
			concurrent pipelines from 1 to 32.

			Because implementation of a multi-threaded simulator  in Python is 
			expensive, and we have our model integrated in SimGrid, 
			we only compare the results of simulators with original SimGrid, 
			SimGrid integrated with our model and and real pipelines in this 
			experiment. The results are compared in total makespan of the pipelines, 
			cumulative read time and cumulative write time.

@@

		    Since different storage types should also be taken into account, 
		    we conduct another experiment with the same scenario as 
		    in the multi-threaded experiment, except that files are stored on a 
		    shared file system instead of local disk.

		    \textcolor{red}{[Description of Lustre on the cluster and how it's 
		    simulated]}.

		    \subsubsection{Simulation of a real application}

		    Finally, we consider a real pipeline from the neuroimaging domain. 			
			\textcolor{red}{[Description of the real pipeline with nighres 
			(including the workflow engine if it's Dask)]}.

			We simulate this pipeline with a simulator with original SimGrid and 
			extended SimGrid. 
			The simulation results are then compared with the real results. 
			Because our work focuses on I/O time, we assume that CPU time is 
			correctly modeled and use the CPU time measured in the real pipelines 
			to setup our simulated workflow. The results are compared in terms of 
			I/O time and total makespan.
